Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
more captions

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs128comp_20} &
	  \includegraphics[width=.425\textwidth]{vel128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T2.png} &
	  \includegraphics[width=.425\textwidth]{vel_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T3.png} &
	  \includegraphics[width=.425\textwidth]{vel_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for test 4 at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T4.png} &
	  \includegraphics[width=.425\textwidth]{vel_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T5.png} &
	  \includegraphics[width=.425\textwidth]{vel_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T6.png} &
	  \includegraphics[width=.425\textwidth]{vel_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T7.png} &
	  \includegraphics[width=.425\textwidth]{vel_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T8.png} &
	  \includegraphics[width=.425\textwidth]{vel_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T9.png} &
	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T10.png} &	
	  \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T10.png} &	
      \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{density, pressure, and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T11.png} &	
	  \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T11.png} &	
      \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{density, pressure, and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{density (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{density (2000 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_400.png}	
  \end{center}
  \caption{pressure (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_2000.png}	
  \end{center}
  \caption{pressure (2000 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
  \end{center}
  \caption{velocity (400 cells)}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
  \end{center}
  \caption{velocity (2000 cells)}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel128comp_20} &
	  \includegraphics[width=.425\textwidth]{prs128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T2.png} &
	  \includegraphics[width=.425\textwidth]{prs_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T3.png} &
	  \includegraphics[width=.425\textwidth]{prs_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T4.png} &
	  \includegraphics[width=.425\textwidth]{prs_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T5.png} &
	  \includegraphics[width=.425\textwidth]{prs_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T6.png} &
	  \includegraphics[width=.425\textwidth]{prs_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T7.png} &
	  \includegraphics[width=.425\textwidth]{prs_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T8.png} &
	  \includegraphics[width=.425\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T9.png} &
	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T9.png} &	
      \includegraphics[width=.4\textwidth]{prs_T9.png}\\
	\end{tabular}	
  \end{center}
  \caption{Results for the peak problem at $t=0.0039$, computed with 800 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Density is shown in the top two panels at two different zoom levels. The bottom left panel shows velocity, and the bottom right panel shows pressure.}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T10.png} &	
	  \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T10.png} &	
      \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 10 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{vel_T11.png} &	
	  \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
      \includegraphics[width=.4\textwidth]{prs_T11.png} &	
      \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{Results for test 11 at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line. Each pair of side-by-side panels shows the same results at different zoom levels. The top panels show density, the middle show velocity, and the bottom show pressure.}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_400.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_2000.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}
